\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate error-free

\subsection{Visualisation} \label{sec:visualisation}
When implementing geometry a rapid and robust visualisation system is key to produce error free and efficient simulation input.
A  \PYGEOMETRY{}  hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.

>>>>

\subsection{Visualisation} \label{sec:visualisation}
When implementing geometry a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
A  \PYGEOMETRY{}  hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
